Graph Databases for Use with Timeseries IoT Datasets

### 2023-12-05 paper.tex
Aaaaaaaaaaaaaaaaaah
Aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaah

This figure provided a more definitive idea about what was going on for some of the IP Addresses. In particular,
192.168.100.148 contacted the most ports likely indicating that it was performing a network scan on one of the
other networks. Similarily could be said for 192.168.100.149 and 192.168.100.150 with less confidence. This query
was performed by looking at the unique nodes that connected to the IP addresses.

@@

As shown in figure \ref{fig:incomingflows} there is no evidence that any DDoS attacks occured withing this timeframe,
ruling out a DDoS attack as a source of the flows to the IoT device.

>>>>

This figure provided a more definitive idea about what was going on for some of the IP Addresses. This query
was performed by looking at the unique nodes that connected to the IP addresses. In order
to determine whether a network scan had occured, one must look at the number of ports contacted on a particular
device within quick succession in a particular timeframe. If it is an abnormally high number, it is likely a 
network scan attack has occurred. In particular, 192.168.100.148 contacted the most ports at 280 ports total 
being contacted likely indicating that it was performing a network scan on one of the other networks. 
Similarily could be said for 192.168.100.149 and 192.168.100.150 with less confidence at 82 and 127 ports
contacted respectively.

@@

As shown in figure \ref{fig:incomingflows} there are very few flows to any device. All devices in this sample have 
only one or two connections. In order to determine if a DDoS attack had occured within a timeframe, what would have
to be looked for is an abnormally large number of flows coming into a device in order for it to be considered
distributed. Without it, there is no proper way of determaning Denial of Service from flow data alone. 
Thus, there is no evidence that any DDoS attacks occured withing this timeframe, ruling out a DDoS attack as a source 
of the flows to the IoT device.
